\documentclass[10pt,journal,draftclsnofoot,onecolumn]{IEEEtran}
\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage[margin=.75in]{geometry}
\usepackage{courier}
\usepackage{ifthen}
\usepackage{setspace}
\usepackage{listings}
\usepackage[usenames, dvipsnames]{color}
\usepackage{tabularx}
\usepackage[strict]{chngpage}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{acronym}


\acrodef{OSU}[OSU]{Oregon State University}
\acrodef{AIAA}[AIAA]{American Institute of Aeronautics and Astronautics}
\acrodef{AGL}[AGL]{Above Ground Level}

\lstset {
	language=C,
	basicstyle=\ttfamily,
	keywordstyle=\color{blue}\ttfamily,
	stringstyle=\color{red}\ttfamily,
	commentstyle=\color{OliveGreen}\ttfamily,
	morecomment=[l][\color{magenta}]{\#}
	showstringspaces=false,
	showspaces=false,
	frame=single,
	captionpos=b
}

\newcommand{\commandline}[2][\empty] {
	\begin{quote}
		\texttt{#2}
		\ifthenelse{\equal{#1}{\empty}}{}{\begin{quote}#1\end{quote}}
	\end{quote}
}

\begin{document}
	\singlespace
	
	\title{\vspace{2in}Problem Statement}
	
	\author {
		Anisimova, Natasha
		\and
		Lee, Terrance
		\and
		Morgan, Albert
	}
	
	\markboth{CS Capstone 2016-2017}{Assignment 1}
	
	\pagestyle{empty}
	\vspace*{2in}
	\begin{center}
		\huge
		Problem Statement\\
		\normalsize
		\vspace{5mm}
		CS Capstone\\
		Spring 2016\\
		\vspace{5mm}
		Natasha Anisimova\\
		Terrance Lee\\
		Albert Morgan
	\end{center}
	
	\vspace{5mm}
	
	\begin{center}
		\textbf{Abstract}
	\end{center}
	
	\begin{adjustwidth}{2in}{2in}
		In June 2017, the OSU chapter of the
		AIAA will launch a rocket in the Mojave Desert.
		They will be the first university team to launch a rocket into the stratosphere, one hundred thousand feet above 
		sea level.
		Our team will develop the tracking software that receives
		telemetry from the rocket during its flight
		and displays the data in real-time for the entire OSU rocketry team.
		This software must be flexible, robust, and accurate in order
		to ensure that the variety of engineers on the project all receive
		the data they need on launch data.
		This document will give an overview of the problem,
		our proposed solution,
		and describe how we will measure its success.
	\end{adjustwidth}
	
	\newpage
	\pagestyle{headings}
	\section{Problem Definition}
	In June 2017, the \ac{OSU} chapter of the
	\ac{AIAA} will launch a rocket in the Mojave Desert.
	This rocket will ascend to one hundred thousand feet \ac{AGL}.
	Designing, building, and launching the rocket will require the
	collaboration and expertise of dozens of engineers from a variety
	of disciplines, including mechanical, electrical, computer, and
	software.
	
	While the rocket is in flight, the \ac{OSU} rocketry team
	must be able to receive, view, and store telemetry in real-time.
	Mission critical information that must be received by the ground
	station are latitude, longitude, and altitude. The latitude
	and longitude will aid in tracking and recovery of the rocket
	after flight. Real-time altitude readings will allow the rocket
	team to determine if the objective of one hundred thousand feet
	has been met even if recovery of the rocket is impossible.
	
	
	% Use the \subsection command to create a subsection:
	% \subsection{Section title}
	\section{Proposed Solution}

	\subsection{The Ground Station}

	With the aid of the computer engineers in the avionics team,
	the software team will design, build, and deploy a ground station
	capable of receiving and displaying essential telemetry in real time.
	At a minimum, this telemetry includes highest recorded altitude and
	last known latitude and longitude.

	The software team proposes building a dedicated ground station,
	to receive, log, and make available telemetry in real-time.
	The avionics team will provide the hardware platform, which should
	have the ability to:

	\begin{itemize}
	\item receive telemetry from the rocket
	\item run a modern multitasking operating system
	\item broadcast a wireless access point
	\item write to non-volatile storage
	\item display data on a screen without external devices
	\end{itemize}

	The software team will develop a package for the ground station that
	will acquire, format and log the telemetry in real-time.
	Mission critical data will be displayed on the built-in display so that
	no external devices will be necessary to meet the minimum requirements.
	This data will be logged to non-volatile storage, so it may be
	downloaded onto another device at a later time.
	
	\subsection{Desired Features}

	After the primary objectives outlined in the previous section
	are met, there are a number of optional features
	that have been requested by the \ac{OSU} rocketry team.
	Because the reliability of this software is essential on launch day,
	additional features will only be implemented after
	the stability, robustness, and accuracy of previous features
	is ensured.

	A customized web server will be developed for the ground station,
	and the rocketry team will be able to connect to the ground station
	though a wireless access point. Once connected, data will be able
	to be viewed in real-time in a graphical format through their
	web browser.

	The software team will work closely with the engineers in the
	rest of the rocketry team to ensure the software
	meets their needs on launch day. These features will be considered
	and prioritized at a later date, but should never compromise the stability,
	robustness, and accuracy of the system or its ability
	to display the essential telemetry.
	
	\subsection{Launch Simulation}
	
	The mechanical engineers of the group have requested a launch simulator that
	would allow them to control sensors on-board the rocket in order to test
	systems that rely on certain sensor data. This will consist of a separate
	software package that will only be designed and implemented after the
	essential features of the ground station are complete. The launch simulator
	will be prioritized along with the other desired features at a later date.

	\subsection{Expo}
	At the engineering expo, the software team will demonstrate their software
	in a simulated environment. This may include replaying real data from test launches
	or using hand-crafted data.
	If the desired web server function is complete, then people will be given the ability
	to connect to our server with their personal computers and view the data themselves.
	Ideally, this would be done by working closely
	with the avionics team to highlight the combined achivements of our
	hardware and software.
	
	\section{Performance Metrics}
	
	The successfulness of the project will measured by whether the data
	is successfully recorded and made accessible to the rocketry team
	on launch day. To ensure the software is ready for launch day,
	we will consider three primary performance metrics:
	
	\begin{itemize}
		\item Stability: the software should not crash or otherwise cease operation
		\item Robustness: the software should handle bad inputs gracefully
		\item Accuracy: the software should correctly report all telemetry
	\end{itemize}
	
	In order to meet these requirements, a comprehensive test plan will
	be written and executed. This plan will involve sending large amounts
	of random, recorded, and live data to the software and recording the results.
	The software will only be considered successful if it passes all of these
	tests with no errors.
	
\end{document}


